\chapter*{Abstract}

Companies like LG have introduced smart refrigerators in recent years; refrigerators that can be controlled via mobile phone and allow the products to meet inside through smart labels.

The project aims to bring some of this technology to you without having to make a large investment. No need to change refrigerators, for it was created by a component \emph{Arduino}, which allows escamear products are introduced or consume the refrigerator.

There are applications that allow bring spending at home, but unlike this project are focused and include the total cost of a purchase. This project allows you to scan product by product, and thanks to a collaborative data base, to obtain the total cost of the purchase; distinguished by type of food will be available ... Also eating habits, check that products are missing, create a shopping list, etc.

This solution was divided into three main blocks:

 \begin{description}
    \item Electronic Component

        It is part of the more physical project which has created a device that allows reading products.

        To do this it has two input modes products; through barcode or an RFID tag, and a wireless output to communicate to the server input products.

    \item Centralized Server

        It is the logic of the project, responsible for receiving electronic component information, store it and run with it to provide client applications access to all information.

    \item Client Application

            It is the communication part where all the information is consumed by the user through graphical summaries, lists, etc.

            By crossing data generated by the electronic component and all information contained on the server will show the customer the following information:
            \begin{itemize}
                \item Current Stock of the fridge
                \item Consumption statistics; lists and statistics with the products purchased using filters like; product, dates, prices...
                \item Expenditure statistics
            \end{itemize}

            By using a centralized server will allow the creation of tools for collaboration between users of the application for the creation and management:

            \begin{itemize}
                \item Product identification; name, price, image, etc.
                \item Purchase plans; allow share purchase plans that can be adjusted to achieve different purposes like saving money.
                \item Recipes; this way you can see based on the stock that you have in the fridge which recipes can be prepared.
            \end{itemize}
\end{description}